The Semantics and Implementation of \CEU: a Synchronous Reactive Language based on Esterel

### 2015-09-19 paper.tex
Nome da secao 2.2

In the sections that follow, we review the main differences between \CEU and 
Esterel~\cite{ceu.sensys13}:
stack-based internal events (Section~\ref{sec.ceu.ints}),
shared-memory concurrency (Section~\ref{sec.ceu.det}),
safe abortion with finalization (Section~\ref{sec.ceu.abrt}),
and first-class timers (Section~\ref{sec.ceu.timers}).

@@

%\newpage %TTT
\subsection{Shared-Memory Concurrency}
\label{sec.ceu.det}

>>>>

In the sections that follow, we review the main differences between \CEU and 
Esterel~\cite{ceu.sensys13}:
stack-based internal events (Section~\ref{sec.ceu.ints}),
shared-memory concurrency and determinism (Section~\ref{sec.ceu.det}),
safe abortion with finalization (Section~\ref{sec.ceu.abrt}),
and first-class timers (Section~\ref{sec.ceu.timers}).

@@

%\newpage %TTT
\subsection{Shared-Memory Concurrency and Determinism}
\label{sec.ceu.det}
